Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box

### 2015-05-05 paper/paper 2/paper 2.tex
RDF-CV semantics

%The underlying \emph{semantics} for RDF validation is \emph{UNA} and \emph{CWA}.
RDF validation requires that different names represent different objects (\emph{\textbf{unique name assumption (UNA)}}), whereas,
\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
A data property is \emph{functional} (\emph{R-65}) if for each individual \emph{x}, there can be at most one distinct literal \emph{y} such that \emph{x} is connected by the data property to \emph{y}. 
When assuming \emph{UNA}, the functional property {\em title} (\ms{funct (title)}) causes a clash
in case the book {\em Huckleberry-Finn} has more than one \emph{title}
(\ms{title(Huckleberry-Finn, The-Adventures-of-Huckleberry-Finn)}, \ms{title(Huckleberry-Finn, Die-Abenteuer-des-Huckleberry-Finn)}).
Assuming nUNA, however, reasoning concludes that the titles {\em The-Adventures-of-Huckleberry-Finn} and {\em Die-Abenteuer-des-Huckleberry-Finn} are the same (\ms{\{The-Adventures-of-Huckleberry-Finn\}} = \ms{\{Die-Abenteuer-des-Huckle} \ms{berry-}\ms{Finn\}}).

>>>>

%The underlying \emph{semantics} for RDF validation is \emph{UNA} and \emph{CWA}.
RDF validation requires that different names represent different objects (\emph{\textbf{unique name assumption (UNA)}}), whereas,
\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
A data property is \emph{functional} (\emph{R-65}) if for each individual \emph{x}, there can be at most one distinct literal \emph{y} such that \emph{x} is connected by the data property to \emph{y}. 
When assuming \emph{UNA}, the functional property {\em title} (\ms{funct (title)}) causes a clash
in case the book {\em Huckleberry-Finn} has more than one \emph{title}.
%(\ms{title(Huckleberry-Finn,} \ms{The-Adventures-of-Huckleberry-Finn)}, \ms{title} \ms{(Huckleberry-Finn,} \ms{Die-Abenteuer-des-Huckleberry-Finn)}).
Assuming \emph{nUNA}, however, reasoning concludes that the titles {\em The-Adventures-of-Huckleberry-Finn} and {\em Die-Abenteuer-des-Huckleberry-Finn} are the same. 
%(\ms{\{The-Adventures-of-Huckleberry-Finn\}} = \ms{\{Die-Abenteuer-des-Huckle} \ms{berry-}\ms{Finn\}}).
